Wrangle transcripts

### 2025-10-18 code/expt_3/data_prep_3.Rmd
start transcripts for expt 3

less_raw_data <- raw_data %>%
  select(target, distractor, trialNum, targetNum, repNum, response, correct, time, listener = playerId, speaker, gameId) %>%
  mutate(across(c(target, distractor, response), ~ label_image(.x))) %>%
  write_csv(here("data/expt_2/clean_data.csv"))
```

>>>>

less_raw_data <- raw_data %>%
  select(target, distractor, trialNum, targetNum, repNum, response, correct, time, listener = playerId, speaker, gameId) %>%
  mutate(across(c(target, distractor, response), ~ label_image(.x))) %>%
  write_csv(here("data/expt_3/clean_data.csv"))
```
